Empirical Bayes analysis of \RNAseq{} data for detection of gene expression heterosis

### 2015-05-13 ebayes_rnaseq_heterosis.tex
starting to update for eBayes

@@

We present a hierarchical model for the normalization factors, overdispersions, and gene-specific mean parameters. The normalization factors, parental averages, and overdispersion parameters are assumed to follow a normal distribution, i.e.
\[ 
\gamma_{vi} \stackrel{ind}{\sim} N(0,\sigma_\gamma^2), \quad 
\phi_g \stackrel{ind}{\sim} N(\eta_\phi, \sigma_\phi^2), \quad \mbox{and}\quad 
\psi_g \stackrel{ind}{\sim} N(0,\sigma_\psi^2). 
\]
To allow for more shrinkage with the half-parental and hybrid differences, we use a Laplace (or double exponential prior) and thus implement a Bayesian LASSO \citep{park2008bayesian}, i.e. 
\[ 
\alpha_g \stackrel{ind}{\sim} La(\eta_\alpha, \sigma_\alpha) \qquad \mbox{and} \qquad
\delta_g \stackrel{ind}{\sim} La(\eta_\delta, \sigma_\delta) 
\]
where $\alpha\sim La(\eta,\sigma)$ has a probability density function given by $p(\alpha|\eta,\sigma) = \exp(-|\alpha-\eta|/\sigma)/2\sigma$, expectation $\eta$, and variance $2\sigma^2$. We assume independence amongst the normalization factors, parental averages, half parental differences, hybrid differences, and overdispersion parameters.

>>>>

\renewcommand{\gamma}{c}

@@

We present a hierarchical model for the gene-specific mean parameters and overdispersion parameters. The parental averages and overdispersion parameters are assumed to follow a normal distribution, i.e.
\[ 
%\gamma_{vi} \stackrel{ind}{\sim} N(0,\sigma_\gamma^2), \quad 
\phi_g \stackrel{ind}{\sim} N(\eta_\phi, \sigma_\phi^2), \quad \mbox{and}\quad 
\psi_g \stackrel{ind}{\sim} N(0,\sigma_\psi^2). 
\]
To allow for more shrinkage with the half-parental and hybrid differences, we use a Laplace (or double exponential prior) and thus implement a Bayesian LASSO \citep{park2008bayesian}, i.e. 
\[ 
\alpha_g \stackrel{ind}{\sim} La(\eta_\alpha, \sigma_\alpha) \qquad \mbox{and} \qquad
\delta_g \stackrel{ind}{\sim} La(\eta_\delta, \sigma_\delta) 
\]
where $\alpha\sim La(\eta,\sigma)$ has a probability density function given by $p(\alpha|\eta,\sigma) = \exp(-|\alpha-\eta|/\sigma)/2\sigma$ with expectation $\eta$ and variance $2\sigma^2$. We assume independence amongst the normalization factors, parental averages, half parental differences, hybrid differences, and overdispersion parameters.
